{\bf Practical Concurrency Testing}

### 2018-10-12 thesis/defense/snakefight.tex
snakefight finish educ section and write some tsx, mostly bonus slides

\begin{frame}{Setting}
	CMU (15-410, S'15-S'18), PSU (CMPSC 473, S'18)
	\begin{itemize}
		\item Thread library (``P2'')
			\begin{itemize}
				\item POSIX-like userspace thread library %(also teams of 2)
				\item Reference ``Pebbles'' kernel provided
					% say: later they implement this in p3
				\item Fixed APIs $\rightarrow$ instrumentation can be automated
				\item Still needs heuristics to handle ad-hoc synchronization
			\end{itemize}
			% FIXME: need introduce p3 here?
	\end{itemize}
	\pause
	\linegap

@@

		%\item Processes (``userprog'')
		%\begin{itemize}
				% fork is part of exec and the loader is already provided
			\item ``userprog'': UNIX-like process lifecycle
				%({\tt exec},
				({\tt exit}, {\tt wait})
			%\item File descriptor management ({\tt create}, {\tt remove}, {\tt open}, {\tt read}, ...)
				% filesys project is beyond scope of landslide
				% DONT say: the u chicago professor chose to discard the hard concurrency parts
				% DO say, if pressured: device driver concurrency would require more engineering,
				% so we chose to limit it to these two projex
		\end{itemize}
	\end{itemize}
\end{frame}

\begin{frame}{Instrumentation}
	% Unlike kernels [Blum '12], P2 can be......
	% TODO talk abt yield loops, 
	% compare to prior technique - delay abounding - which sucks bc (verify this by reading BPOR) it doesn't actually
	% wake up the other thread at the right time (using memory conflix)

@@

@@

\begin{frame}{Statistical Significance}
	Compared users' vs. non-users' grade distributions with k-sample Anderson-Darling {\em [Anderson, Darling '52]}
	\linegap

@@

\begin{frame}{Example}
	\begin{center}
		\begin{tabular}{l}
			\texttt{if ((status = \_xbegin()) == \_XBEGIN\_STARTED) \{} \\
			%\texttt{} \\
			%\texttt{} \\
			\texttt{~~~~foo++;} \\
			\texttt{~~~~\_xend();} \\
			\texttt{\} else \{}\\ %if (status != \_XABORT\_EXPLICIT) \{} \\
			\texttt{~~~~mutex\_lock(\&foo\_lock);} \\
			\texttt{~~~~foo++;} \\
			\texttt{~~~~mutex\_unlock(\&foo\_lock);} \\
			\texttt{\}} \\
		\end{tabular}
	\end{center}
\end{frame}

\begin{frame}{HTM Execution Semantics}
	Attempting a transaction
	\begin{itemize}
		\item Code between \xbegin and \xend is provisionally executed
		\item All writes kept in cache until \xend
		\item \xend commits changes atomically (w.r.t. other CPUs)
	\end{itemize}
	\pause
	\linegap

@@

\begin{frame}{Model Checking Transactional Programs}
	What does it mean to MC a program?
	\begin{itemize}
		\item Capture all sites of nondeterminism as preemption points
		\item Control nondeterminism to force each possibility at each point
		\item (Identify equivalences to prune unnecessary preemption points)
	\end{itemize}
	\pause
	\linegap

@@

\begin{frame}{Concurrency model}
	What are a transactional program's {\em observable} behaviours?
	\begin{itemize}
		\item Transactional writes, if successful, appear atomically %to other threads
		\begin{itemize}
			\item Equivalent to a lock protecting that state
				% note that also inserting DR PPs within a transaction is not allowed
		\end{itemize}
			\pause
		\item Simultaneous transactions succeed only if no conflicts
		\begin{itemize}
			\item Equivalent
				%(modulo performance)
				to serialize independent transactions
		\end{itemize}
			\pause
		\item Failing transactions' effects rolled-back with no trace
		\begin{itemize}
			\item Treat each \xbegin as a failure injection point
		\end{itemize}
	\end{itemize}
\end{frame}

\begin{frame}{Failure Injection - 2 dimensions of concurrency}
	\begin{center}
		\includegraphics[width=\textwidth]{failure-injection-0.pdf}
	\end{center}
\end{frame}
\begin{frame}{Failure Injection - 2 dimensions of concurrency}
	\begin{center}
		\includegraphics[width=\textwidth]{failure-injection-2.pdf}
	\end{center}
\end{frame}

\begin{frame}{Deliverables}
	In the thesis, I will:
	\begin{itemize}
		\item Implement the HTM(-equivalent) concurrency model in Landslide
		\item Extend the model to support STM
		\item Prove equivalence to HTM/STM semantics % under MC
		\item Bugfind/verify a suite of unit tests \& real-world TM programs
	\end{itemize}
\end{frame}

@@

\section{End}

\breakslide{\Large Q\&A
%\linegap
%
%\begin{center}
%	\includegraphics[width=0.65\textwidth]{3word-questions.png}
%\end{center}
}

@@

\section{Bonus Slides}

\breakslide{\Large Bonus Slides}

\begin{frame}{HTM: Even more dimensions of nondeterminism}
	% The gotcha: When xbegin can fail, it can emit diff error codes, which depend on what happened within.
	\begin{center}
		\begin{tabular}{l}
			\texttt{if ((status = \_xbegin()) == \_XBEGIN\_STARTED) \{} \\
			\texttt{~~~~if (count < 100)}\\
			\texttt{~~~~~~~~\_xabort();} \\
			\texttt{~~~~count++;} \\
			\texttt{~~~~\_xend();} \\
			\texttt{\} else if (status != \_XABORT\_EXPLICIT) \{} \\
			\texttt{~~~~mutex\_lock(\&count\_lock);} \\
			\texttt{~~~~count++;} \\
			\texttt{~~~~mutex\_unlock(\&count\_lock);} \\
			\texttt{\}} \\
		\end{tabular}
	\end{center}
	\linegap

	\xbegin can fail with multiple possible error codes
	\begin{itemize}
		\item MC will identify on-the-fly when (e.g.) {\tt \_XABORT\_EXPLICIT} is possible
		\item Treat such transactions as having multiple failure injection possibilities
		\item Future work: dataflow analysis to identify when failure reason never used
	\end{itemize}
\end{frame}

\begin{frame}{HTM: Sources of Benchmarks}
	\begin{itemize}
		%\item Shamay, https://github.com/cmpxchg16/tsx.me, 2014
		\item Dehesa-Azuara and Stanley, http://www.contrib.andrew.cmu.edu/\textasciitilde{}mdehesaa/, 2016
		%\item Chapman et al., Hybrid STM/HTM for nested transactions on OpenJDK, OOPSLA 2016
		%\item Wang et al., Eunomia: Scaling Concurrent Search Trees under Contention Using HTM, PPoPP 2017
			% TODO: add, that one lock thingy
	\end{itemize}
\end{frame}

%%%%

@@

\breakslide{\Large Super Extra Bonus Slides Copy-Pasted from OOPSLA}

@@

% TODO: slide number c.c
\begin{frame}{Don't you need \texttt{if (mutex\_held(\&foo\_lock)) \_xabort();} in that transaction on slide 31?}
	Yes.
\end{frame}

\begin{frame}{References}
	\small
	\begin{itemize}
		\item {\bf [Lamport '78]}:
			Leslie Lamport. Time, clocks, and the ordering of events in a distributed system.
			Commun. ACM, 1978.
		\item {\bf [Godefroid '97]}: Patrice Godefroid.
			VeriSoft. A tool for the automatic analysis of concurrent reactive software. CAV 1997.
		%\item {\bf [Holzmann '97]}: The model checker SPIN. TOSE 1997.
		\item {\bf [Engler '03]}: Dawson Engler and Ken Ashcraft.
			RacerX: effective, static detection of race conditions and deadlocks. SOSP 2003.
		\item {\bf [O'Callahan '03]}: Robert O'Callahan and Jong-Deok Choi.
			Hybrid dynamic data race detection. PPoPP '03.
		\item {\bf [Flanagan '05]}: Cormac Flanagan and Patrice Godefroid. Dynamic partial-order reduction for
			model checking software. POPL 2005.
		\item {\bf [Musuvathi '08]}: Madanlal Musuvathi et al. Finding and Reproducing Heisenbugs in Concurrent
			Programs. OSDI 2008.
		\item {\bf [Yang '08]}: Yu Yang et al. Efficient stateful dynamic partial order reduction. SPIN 2008.
	\end{itemize}
\end{frame}
\begin{frame}{References}
	\small
	\begin{itemize}
		\item {\bf [Buckhardt '10]}: A randomized scheduler with probabilistic guarantees of finding bugs. ASPLOS 2010.
		\item {\bf [Simsa '12]}: Jiri Simsa. Runtime Estimation and Resource Allocation for
			Concurrency Testing. CMU-PDL-12-113. December 2012.
		\item {\bf [Blum '12]}: Ben Blum. Landslide: Systematic Dynamic Race Detection in Kernel
			Space. CMU-CS-12-118. May 2012.
		\item {\bf [Kasicki '12]}: Baris Kasicki. Data races vs. data race bugs: telling the difference with Portend. ASPLOS '12.
		\item {\bf [Huang '15]}: Jeff Huang. Stateless model checking concurrent programs with maximal causality reduction. PLDI '15.
		\item {\bf [Jensen '15]}: Stateless Model Checking of Event-Driven Applications. OOPSLA 2015.
	\end{itemize}
\end{frame}

>>>>

\begin{frame}{Setting}
	CMU (15-410, S'15-S'18), PSU (CMPSC 473, S'18)
	\begin{itemize}
		\item Thread library (``P2'')
			\begin{itemize}
				\item POSIX-like userspace thread library %(also teams of 2)
				\item Reference ``Pebbles'' kernel provided
					% say: later they implement this in p3
				\item Fixed APIs $\rightarrow$ instrumentation can be automated
				\item Still needs heuristics to handle ad-hoc synchronization
			\end{itemize}
			% FIXME: need introduce p3 here?
			% Or cut?
		\item Kernel (``P3'') - reimplement said reference kernel (CMU only)
	\end{itemize}
	\pause
	\linegap

@@

		%\item Processes (``userprog'')
		%\begin{itemize}
				% fork is part of exec and the loader is already provided
			\item ``userprog'': UNIX-like process lifecycle
				({\tt exec}, % students don't really implement any complciated part of this though
				% i think just like. the argument copying??
				{\tt exit}, {\tt wait})
			%\item File descriptor management ({\tt create}, {\tt remove}, {\tt open}, {\tt read}, ...)
				% filesys project is beyond scope of landslide
				% DONT say: the u chicago professor chose to discard the hard concurrency parts
				% DO say, if pressured: device driver concurrency would require more engineering,
				% so we chose to limit it to these two projex
		\end{itemize}
	\end{itemize}
\end{frame}

\begin{frame}{Instrumentation}
	Understanding concurrency primitives/APIs
	\begin{itemize}
		\item Kernel-level testing requires manual annotation {\em [Blum '12]}
		\item P2 (fixed APIs), Pintos (basecode provided) annotated automatically
	\end{itemize}
	\pause
	\linegap

	Ad-hoc synchronization (e.g. {\tt while (!ready) yield();})
	\begin{itemize}
		\item Not an infinite loop bug!
		\item Heuristically ``block'' threads when 10+ {\tt yield()}s %({\tt xchg}, etc.)
		\item Existing memory analysis %(DPOR)
			on loop condition to unblock
			\begin{itemize}
					% TODO: cut this and just say it out loud?
				\item (e.g., what other thread writes to {\tt ready}?)
				% it's kinda... idk how to critique its unsoundness.
				% they self-admit to the unsoundness but like, leaving the cycle in,
				% is the wrong approach to begin with
				\item Prior work {\em [Coons '13]} likely to leave threads blocked too long
			\end{itemize}
		\item Check for false-positive blocking to avoid false-positive deadlocks
	\end{itemize}

	% Unlike kernels [Blum '12], P2 can be......
	% TODO talk abt yield loops, 
	% compare to prior technique - delay abounding - which sucks bc (verify this by reading BPOR) it doesn't actually
	% wake up the other thread at the right time (using memory conflix)

@@

\begin{frame}{Effect on Grades}
	\begin{center}
		\includegraphics[width=\textwidth]{photo-of-ze-studence-cdf-no-pre-study.pdf}
	\end{center}
\end{frame}

@@

\begin{frame}{Statistical Significance}
	Compared %users' vs. non-users'
	grade distributions with k-sample Anderson-Darling {\em [A., D. '52]}
	\linegap

@@

\begin{frame}{Example}
	\begin{center}
		\begin{tabular}{l}
			\texttt{if ((status = \_xbegin()) == SUCCESS) \{} \\ %\_XBEGIN\_STARTED) \{} \\
			%\texttt{} \\
			%\texttt{} \\
			\texttt{~~~~count++;} \\
			\texttt{~~~~\_xend();} \\
			\texttt{\} else \{}\\ %if (status != \_XABORT\_EXPLICIT) \{} \\
			\texttt{~~~~mutex\_lock(\&count\_lock);} \\
			\texttt{~~~~count++;} \\
			\texttt{~~~~mutex\_unlock(\&count\_lock);} \\
			\texttt{\}} \\
		\end{tabular}
	\end{center}
\end{frame}

\begin{frame}{HTM Execution Semantics}
	Attempting a transaction
	\begin{itemize}
		\item Code between \xbegin and \xend is provisionally executed
		\item All writes kept in CPU cache until \xend
		\item \xend commits changes atomically (w.r.t. other CPUs)
	\end{itemize}
	\pause
	\linegap

@@

\begin{frame}{Model Checking Transactional Programs}
	What does it mean to MC a program?
	\begin{itemize}
		\item Capture all sites of nondeterminism as preemption points
		\item Control nondeterminism to force each possibility at each point
			\begin{itemize}
				\item (identifying equivalences to prune redundant branches)
			\end{itemize}
	\end{itemize}
	\pause
	\linegap

@@

\begin{frame}{Example}
	\begin{center}
		\begin{tabular}{l|l}
			{\bf Thread 1} & {\bf Thread 2} \\
			\hline
			{\tt \_xbegin() == SUCCESS} \\
			{\tt count++;} \\
				& {\tt \_xbegin() == SUCCESS} \\
				& {\tt count++;} \\
				& {\tt xend();} \\
			{\tt xend()}...? \\
			{\em <conflict detected>} \\
			\\
			{\tt \_xbegin() == FAIL} \\
			{\tt mutex\_lock(...);} \\
			{\tt count++;} \\
			{\tt mutex\_unlock(...);} \\
		\end{tabular}
	\end{center}
\end{frame}

\begin{frame}{Concurrency model}
	What are a transactional program's {\em observable} behaviours?
	\begin{itemize}
		\item Transactional writes, if successful, appear atomically %to other threads
		\begin{itemize}
			\item Equivalent to a lock protecting that state
				% note that also inserting DR PPs within a transaction is not allowed
		\end{itemize}
			\pause
		\item Simultaneous transactions succeed only if no conflicts
		\begin{itemize}
			\item Equivalent
				%(modulo performance)
				to serialize independent transactions
		\end{itemize}
			\pause
		\item Failing transactions' effects rolled-back with no trace
		\begin{itemize}
			\item Treat each \xbegin as a failure injection point
		\end{itemize}
	\end{itemize}
	\pause
	\linegap

	Equivalence theorem
	\begin{itemize}
		\item Safe to automatically skip all interleavings within transactions
			\begin{itemize}
				\item Exponential state space reduction
				\item Traditional reduction (DPOR) applied on top
			\end{itemize}
		\item More in bonus slides...
	\end{itemize}
\end{frame}

\begin{frame}{Failure Injection - 2 dimensions of concurrency}
	\begin{center}
		\includegraphics[width=\textwidth]{failure-injection-0.pdf}
	\end{center}
\end{frame}
\begin{frame}{Failure Injection - 2 dimensions of concurrency}
	\begin{center}
		\includegraphics[width=\textwidth]{failure-injection-1.pdf}
	\end{center}
\end{frame}
\begin{frame}{Failure Injection - 2 dimensions of concurrency}
	\begin{center}
		\includegraphics[width=\textwidth]{failure-injection-2.pdf}
	\end{center}
\end{frame}

\begin{frame}{Evaluation}
\end{frame}

@@

\section{Conclusion}

\breakslide{
\begin{center}
	% TODO: replace with HIL for honban
	\Large Q\&A
	%\includegraphics[width=0.4\textwidth]{../how-i-learned.png}
\end{center}
%\linegap
%
%\begin{center}
%	\includegraphics[width=0.65\textwidth]{3word-questions.png}
%\end{center}
}

@@

@@

\subsection{Quicksand}
\breakslide{\Large Bonus Slides - Quicksand}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Education}
\breakslide{\Large Bonus Slides - Education}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{HTM}
\breakslide{\Large Bonus Slides - HTM}

\begin{frame}{HTM: Even more dimensions of nondeterminism}
	% The gotcha: When xbegin can fail, it can emit diff error codes, which depend on what happened within.
	\begin{center}
		\begin{tabular}{l}
			\texttt{if ((status = \_xbegin()) == \_XBEGIN\_STARTED) \{} \\
			\texttt{~~~~if (count >= 100)}\\
			\texttt{~~~~~~~~\_xabort();} \\
			\texttt{~~~~count++;} \\
			\texttt{~~~~\_xend();} \\
			\texttt{\} else if (status != \_XABORT\_EXPLICIT) \{} \\
			\texttt{~~~~mutex\_lock(\&count\_lock);} \\
			\texttt{~~~~count++;} \\
			\texttt{~~~~mutex\_unlock(\&count\_lock);} \\
			\texttt{\}} \\
		\end{tabular}
	\end{center}
	\linegap

	\xbegin can fail with multiple possible error codes
	\begin{itemize}
		\item MC will identify on-the-fly when (e.g.) {\tt \_XABORT\_EXPLICIT} is possible
		\item Treat such transactions as having multiple failure injection possibilities
		\item Future work: dataflow analysis to know when failure reason never used
	\end{itemize}
\end{frame}

\begin{frame}{HTM: Sources of Benchmarks}
	\begin{itemize}
		%\item Shamay, https://github.com/cmpxchg16/tsx.me, 2014
		\item Dehesa-Azuara and Stanley, http://www.contrib.andrew.cmu.edu/\textasciitilde{}mdehesaa/, 2016
		%\item Chapman et al., Hybrid STM/HTM for nested transactions on OpenJDK, OOPSLA 2016
		%\item Wang et al., Eunomia: Scaling Concurrent Search Trees under Contention Using HTM, PPoPP 2017
			% TODO: add, that one lock thingy
		\item vamsikc, TSX LevelDB implementation, https://github.com/vamsikc/leveldb-tsx/, 2014
	\end{itemize}
\end{frame}

\definecolor{lavender}{RGB}{102,65,208} % (?? i don't know what happened here anymore but it looks good)
\definecolor{seafoam}{RGB}{56,158,68} % * 2/3
\definecolor{salmon}{RGB}{208,89,74} % * 7/8
\definecolor{goldish}{RGB}{128,96,32}
\newcommand\tii{\ensuremath{\hilight{lavender}{\mathbf{Ti}}}\xspace}
\newcommand\tjj{\ensuremath{\hilight{seafoam}{\mathbf{Tj}}}\xspace}
\newcommand\tkk{\ensuremath{\hilight{salmon}{\mathbf{Tk}}}\xspace}

\newcommand\tiiat[1]{\ensuremath{\hilight{lavender}{\mathbf{Ti}@#1}}\xspace}
\newcommand\tjjat[1]{\ensuremath{\hilight{seafoam} {\mathbf{Tj}@#1}}\xspace}
\newcommand\tkkat[1]{\ensuremath{\hilight{salmon}  {\mathbf{Tk}@#1}}\xspace}

\begin{frame}{HTM failure injection equivalence}
		For any interleaving %prefix
	\[
	\begin{tabular}{c}
		$\tiiat{\alpha},\tiiat{\beta_1}\dots\tiiat{\beta_b},$\\
		$\tjjat{\gamma_1}\dots\tjjat{\gamma_j},$ \\
		$\tkkat{\kappa_1}\dots\tkkat{\kappa_k},$ \\
		$\tiiat{\beta_{b+1}}$ % $\dots\tiiat{\beta_{n-1}}$ -- excluded bc might abort
	\end{tabular}
	\]
	with $b<n$, $j \ne i$, $k \ne i$, etc., either:
	\begin{enumerate}
		\item $\tiiat{\alpha},\tjjat{\gamma_1}\dots\tjjat{\gamma_j},\tkkat{\kappa_1}\dots\tkkat{\kappa_k},\tiiat{\phi_1}\dots$
			\begin{itemize}
				\item (conflicting case), or
			\end{itemize}
		\item $\tiiat{\alpha},\tiiat{\beta_1}\dots\tiiat{\beta_b}\dots\tiiat{\beta_n},\tjjat{\gamma_1}\dots\tjjat{\gamma_j},\tkkat{\kappa_1}\dots\tkkat{\kappa_k}$
			\begin{itemize}
				\item (independent case)
			\end{itemize}
	\end{enumerate}
	exists and is observationally equivalent.
\end{frame}
\begin{frame}{HTM data-race soundness}
	Let:
	\begin{itemize}
		\item
			$\tiiat{\mu},\tjjat{\nu}$ be a memory conflict in an interleaving $\mathcal{I}$
		\begin{itemize}
			\item (normalized under failure injection equivalence)
		\end{itemize}
		\item
		$\mathsf{lockify}_m(\mathcal{I})$ be a function over interleavings
			\begin{itemize}
				\item replaces {\tt xbegin} with {\tt mutex\_lock}($m$) (if successful)
				\item replaces {\tt xend} with {\tt mutex\_unlock}($m$)
			\end{itemize}
		%$\tkkat{L}$ with $\tkkat{\mathsf{lock}(m)}$ if $L$ is a successful HTM begin,
		%with a no-op if $L$ is a transaction abort,
		%or with $\tkkat{\mathsf{unlock}(m)}$ if $L$ is an HTM end,
		%or no replacement otherwise.
		\item
			$\mathcal{I}' = \exists m. \mathsf{lockify}_m(\mathcal{I})$,
			\begin{itemize}
				\item $m$ represents a unique abstract global lock
				\item (failure injection equivalence guarantees mutual exclusion of $m$)
			\end{itemize}
	\end{itemize}
	\linegap

	Then $\tiiat{\mu},\tjjat{\nu}$ is a data race in $\mathcal{I}$ iff it is a data race in $\mathcal{I}'$.
\end{frame}

\begin{frame}{Retry Reduction}
	% TODO: split this into a step by step
	\begin{center}
		\includegraphics[width=\textwidth]{../retry-sets.pdf}
	\end{center}
\end{frame}

% TODO: slide number c.c
\begin{frame}{Don't you need \texttt{if (mutex\_held(\&count\_lock)) \_xabort();} in that transaction on slide 42?}
	\begin{center}
	Yes.
	\end{center}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Bibliography}

\begin{frame}{References}
	\footnotesize
	\begin{itemize}
		\item {\bf [A., D. '52]}: T. Anderson and D. Darling.
			Asymptotic theory of certain ``goodness-of-fit'' criteria based on stochastic processes.
			Annals of Statistics, 1952.
		\item {\bf [Lamport '78]}:
			Leslie Lamport. Time, clocks, and the ordering of events in a distributed system.
			Commun. ACM, 1978.
		\item {\bf [Godefroid '97]}: Patrice Godefroid.
			VeriSoft. A tool for the automatic analysis of concurrent reactive software. CAV 1997.
		%\item {\bf [Holzmann '97]}: The model checker SPIN. TOSE 1997.
		\item {\bf [Engler '03]}: Dawson Engler and Ken Ashcraft.
			RacerX: effective, static detection of race conditions and deadlocks. SOSP 2003.
		\item {\bf [O'Callahan '03]}: Robert O'Callahan and Jong-Deok Choi.
			Hybrid dynamic data race detection. PPoPP '03.
		\item {\bf [Flanagan '05]}: Cormac Flanagan and Patrice Godefroid. Dynamic partial-order reduction for
			model checking software. POPL 2005.
		\item {\bf [Musuvathi '08]}: Madanlal Musuvathi et al. Finding and Reproducing Heisenbugs in Concurrent
			Programs. OSDI 2008.
		\item {\bf [Yang '08]}: Yu Yang et al. Efficient stateful dynamic partial order reduction. SPIN 2008.
	\end{itemize}
\end{frame}
\begin{frame}{References}
	\footnotesize
	\begin{itemize}
		\item {\bf [Buckhardt '10]}: A randomized scheduler with probabilistic guarantees of finding bugs. ASPLOS 2010.
		\item {\bf [Simsa '12]}: Jiri Simsa. Runtime Estimation and Resource Allocation for
			Concurrency Testing. CMU-PDL-12-113. December 2012.
		\item {\bf [Blum '12]}: Ben Blum. Landslide: Systematic Dynamic Race Detection in Kernel
			Space. CMU-CS-12-118. May 2012.
		\item {\bf [Kasicki '12]}: Baris Kasicki. Data races vs. data race bugs: telling the difference with Portend. ASPLOS '12.
		\item {\bf [Coons '13]}: Katherine Coons et al. Bounded Partial Order Reduction. OOPSLA 2013.
		\item {\bf [Huang '15]}: Jeff Huang. Stateless model checking concurrent programs with maximal causality reduction. PLDI '15.
		\item {\bf [Jensen '15]}: Stateless Model Checking of Event-Driven Applications. OOPSLA 2015.
	\end{itemize}
\end{frame}
